Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-12 paper/main.tex
Numbers for 1st 12 minimzed expressions
Remove the 5% number
Add total number of sites

To measure the work performed in \evals, we count the instructions
executed by interpreter during evaluation of the argument. In our
corpus, \EvalEventAllPerc of all instructions (\EventsRnd) are
performed within \eval. Most invocations perform relatively little
work with \Smalleventspct of \evals executing 50 or fewer
instructions. The violin plot of Figure~\ref{ev}(a) corresponds to
\evals executing $\leq$ 50 instructions, it is dominated by trivial
symbol look ups. Figure~\ref{ev}(b) has the work-intensive \evals
which go all the way to \MaxeventsRnd instructions.

@@

\subsection{Things to do}

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me. We should actually remove this number!
\end{itemize}

@@

We classify the resolved expressions to take into account the structure of the expression passed to \eval.
However, we do not want to discriminate expressions based on specific values. Hence, the expression goes through several simplification steps: constant folding of arithmetic and string expressions that use commonly used functions (addition, string concatenation), discarding of specific value to a symbolic value holder, variable absorption. We keep track of variables, as they are evaluated in the environment specified to \eval, contrary to values that are left unchanged.  After the simplification steps, we obtain 15 different \emph{minimized} expressions.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} &  &  &  &  &  \\
		\hline
		\texttt{F(F())} &  &  &  &  &  \\
		\hline
		\texttt{V} &  &  &  &  &  \\
		\hline
		\texttt{F(X)}&  &  &  &  &  \\
		\hline
		\texttt{model.frame} &  &  &  &  &  \\
		\hline
		\texttt{\$}&  &  &  &  &  \\
		\hline
		\texttt{F()}&  &  &  &  &  \\
		\hline
		\texttt{<-} &  &  &  &  &  \\
		\hline
		\texttt{\{BLOCK\}}&  &  &  &  &  \\
		\hline
		\texttt{FUN} &  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
		&  &  &  &  &  \\
		\hline
	\end{tabular}
\end{table}

@@

\section{Case Studies}

\NOTE{5(?) examples from real code?}

\subsection{LEGACY TEXT}

>>>>

To measure the work performed in \evals, we count the instructions
executed by interpreter during evaluation of the argument.  Most invocations perform relatively little
work with \Smalleventspct of \evals executing 50 or fewer
instructions. The violin plot of Figure~\ref{ev}(a) corresponds to
\evals executing $\leq$ 50 instructions, it is dominated by trivial
symbol look ups. Figure~\ref{ev}(b) has the work-intensive \evals
which go all the way to \MaxeventsRnd instructions.

@@

@@

We classify the resolved expressions to take into account the structure of the expression passed to \eval.
However, we do not want to discriminate expressions based on specific values. Hence, the expression goes through several simplification steps: constant folding of arithmetic and string expressions that use commonly used functions (addition, string concatenation), discarding of specific value to a symbolic value holder, variable absorption. We keep track of variables, as they are evaluated in the environment specified to \eval, contrary to values that are left unchanged. We also track whether assignment operators are used in the expression or not. After the simplification steps, we obtain 15 different \emph{minimized} expressions, of which we show the ten first most frequent in numbers of sites in Table~\ref{tab:minimizedexpressions}.

\begin{table}[h]
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Minimized & \#sites & \%sites & \#packages & \#operations & \%envir \\
		\hline
		\texttt{X} & \packageMinimizedcallsitesa  & \packageMinimizedpropsitesa & \packageMinimizedpackagea & \packageMinimizedoperationsaRnd & \packageMinimizedpercentenvira \\
		\hline
		\texttt{F(F())} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedoperationsbRnd & \packageMinimizedpercentenvirb \\
		\hline
		\texttt{V} & \packageMinimizedcallsitesc & \packageMinimizedpropsitesc & \packageMinimizedpackagec & \packageMinimizedoperationscRnd & \packageMinimizedpercentenvirc \\
		\hline
		\texttt{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedoperationsdRnd & \packageMinimizedpercentenvird \\
		\hline
		\texttt{model.frame} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedoperationseRnd & \packageMinimizedpercentenvire \\
		\hline
		\texttt{\$}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedoperationsfRnd & \packageMinimizedpercentenvirf \\
		\hline
		\texttt{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedoperationsgRnd & \packageMinimizedpercentenvirg \\
		\hline
		\texttt{<-} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedoperationshRnd & \packageMinimizedpercentenvirh \\
		\hline
		\texttt{FUN} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedoperationsiRnd & \packageMinimizedpercentenviri \\
		\hline
		\texttt{\{BLOCK\}} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedoperationsjRnd & \packageMinimizedpercentenvirj \\
		\hline
	\end{tabular}
	\caption{Minimized expressions: ten most frequent in terms of sites. \#sites is the number of sites; \%sites the percentage of sites across the total number of sites (\packageNbCallSites sites); \#packages is the number of packages with at least one of the minimized expression and measures how widespread a minimized expression is. \#operations is the average number of steps performed by the R interpreter when given that minimized expression, and \%envir is the percentage of call sites for which the \c{envir} argument is explicitly passed.} \label{tab:minimizedexpressions}
\end{table}

The most common minimized expression is a variable. It happens in \packageMinimizedpropsitesa of the sites and is widespread across packages as it is found in \packageMinimizedpackagea packages across our CRAN corpus. The \c{envir} argument is explicitly passed in \packageMinimizedpercentenvira\% of the call sites, which suggests that \eval is used here to get the value of the variable in a non-local environment.

Note that a site can exhibit several minimized expressions. The most common combinations are:

@@

\section{\eval patterns}

\subsection{Evaluating variables in a specific environment}

\subsection{\c{match.call}}

\subsection{Meta-programming}

\section{LEGACY TEXT}
